---
title: "Project 1: Fall 2024"
execute:
  echo: true
  warning: false
  message: false
  error: true
format: 
  html:
    embed-resources: true
editor: source
---

**Groups**:

- *Group 1:* Maria, Andee, Hailee, Jegg
- *Group 2:* Heather, Chris, Liz, Sara, Jacob
- *Group 3:* Vera, Catherine, Sarlina, Lionel, Killian
- *Group 4:* Curtis, RK, Hooman, Johnny

Consider the emotions from [Inside Out](https://disney.fandom.com/wiki/Inside_Out_2#Cast). [Joy](https://disney.fandom.com/wiki/Joy), [Fear](https://disney.fandom.com/wiki/Fear), and [Ennui](https://disney.fandom.com/wiki/Ennui)  are binge watching Scooby Doo for the first time. After a few episodes, they discuss the probability of unmasking the villain. [Anxiety](https://disney.fandom.com/wiki/Anxiety) has recently taken an interest in Bayesian analysis and decides to exploit this opportunity and play around with the beta-binomial conjugate family. She asks each of her fellow emotions two questions:

* Based on the last 10 episodes you watched, what do you think the probability of unmasking is?

* How certain are you of that probability?

Perpetually bored, [Ennui](https://disney.fandom.com/wiki/Ennui) shrugs when asked each question. Perpetually afraid, [Fear](https://disney.fandom.com/wiki/Fear) implies that he is not very confident that the gang will unmask the villain... and he's not very confident about that, either. Perpetually positive, [Joy](https://disney.fandom.com/wiki/Joy) excitedly says that she's very sure that the probability of unmasking is high - of course the gang will get them!

What do you think the corresponding prior distributions for $\pi$ are?

**Fear:** distribution here

<center>
```{r}

```
</center>

* **Rationale:**  <!--- why did you choose this as the prior for Fear? --->

**Ennui:** distribution here

<center>
```{r}

```
</center>

* **Rationale:** <!--- why did you choose this as the prior for Ennui? --->

**Joy:** distribution here

<center>
```{r}

```
</center>

* **Rationale:** <!--- why did you choose this as the prior for Joy? --->

We will help [Anxiety](https://disney.fandom.com/wiki/Anxiety) perform this analysis! Consider the [Scooby Doo data](https://github.com/rfordatascience/tidytuesday/tree/master/data/2021/2021-07-13), available through Tidy Tuesday. Go ahead and import the data and define a new variable, *unmasked*, that is based on *unmask.fred*, *unmask.daphnie*, *unmask.velma*, *unmask.shaggy*, *unmask.scooby*, *unmask.other*. If any of them taken on the value `"TRUE"`, *unmasked* should take on a 1 (to indicate that the monster was unmasked); otherwise, it should take on a 0 (to indicate that the monster was not unmasked).

```{r}

```

Now, let's create a "year" variable using the `year()` function from the `lubridate` package. Note that the *date.aired* variable contains the original air date of the episode.

```{r}

```

Using the year variable, let's now create a "decade" variable. 

* 1970-1979
* 1980-1989
* 1990-1999
* 2000-2010
* 2010-2019
* 2020-2021

```{r}

```

Each group will consider different aspects of episodes.

Group members will divide and conquer the data categories in their respective areas. The outcome of interest is if the villain was unmasked or not (*unmasked*, created earlier).

In this project, you will:

1. Use the data from 1969 (first season) to update each character's prior. What are their posterior distributions?

2. Perform sequential analysis and update the posterior distribution for each decade that data was collected.

3. Evaluate and describe the progression of beliefs of each emotion.

    - Are the beliefs *different* based on the characteristics explored by your group?
    
        - Note: We have not formally learned Bayesian inference -- I am asking you to use the occular method of analysis for now.

Then, your group will create a 10 minute presentation (yes, with Quarto slides) to discuss the progression of beliefs.

* Because the audience of your presentation is at the same level of understanding, no introductory explanations of Bayesian analysis are necessary.

* Please organize your presentation as you see fit. What is the story that your group wants to tell? Do you want to tell the story character-by-character? Decade-by-decade?

* **Professional development:** Create a gif using [`gganimate`](https://gganimate.com/) that demonstrates the characters' understanding over time.

     
Group 1: Trap Effectiveness
------

**Research Question:** Does the presence of a trap, and subsequently, if it works, increase the probability of unmasking the villain in Scooby Doo episodes?

**Data Categories:** Please use the *trap.work.first* variable to create a "trap" variable that indicates:

* A trap was not set
* A trap was set but did not work
* A trap was set and worked

```{r}

```

Group 2: Character Involvement
------

**Research Question:**
Does Scooby-Doo and Shaggy’s involvement in solving the mystery increase or decrease the likelihood of capturing the villain?

**Data Categories:**
Consider the *caught.shaggy*, *caught.scooby*, *captured.shaggy*, *captured.scooby* variables. "Caught" describes instances where a character physically catches the villain involved in the mystery. "Captured" describes instances where a character apprehends the villain, often after a trap is set. Create variables that indicate the following about the villain:

* Caught or captured by Scooby
* Caught or captured by Shaggy
* Caught or captured by Scooby or Shaggy
* Not caught or captured by Scooby or Shaggy

```{r}

```


Group 3: Number of Villains
------

**Research Question:**
Does the number of villains affect the probability of the gang successfully capturing the villain?

**Data Categories:**
Consider the *monster_amount* variable. Create variables that indicate the following about the episode:

* No monsters
* Only one monster
* Two or three monsters
* Four or more monsters

```{r}

```



Group 4: Villian Motive
------

**Research Question:** Does the villain's motive impact the likelihood of successful capture in Scooby Doo episodes?

```{r}

```

**Data Categories:** Create a new variable that classifies the villain's motive (*motive*) into the following four groups:

* Theft
* Competition
* Conquer, abduction, extortion, or trespassing
* Treasure, smuggling, or inheritance
