---
title: "STA6349: Beta-Binomial"
author: "Your Name Here"
execute:
  echo: true
  warning: false
  message: false
  error: true
format: 
  html:
    embed-resources: true
editor: source
---

<!-- set up chunk, below -->

```{r} 
#| echo: false
library(tidyverse)
library(bayesrules)
```

**Consider a dining survey conducted by a restaurant owner in New York. The owner is also interested in knowing about the proportion $\pi$ of students prefer eating out on Friday. He believes that 40% of the time, $\pi < 0.7$ and 80% of the time, $\pi < 0.9$.**

**1. What do the following prior distributions look like? (i.e., please graph them) Do either (or both) represent the owner's beliefs well?**

**Beta(2, 2):**

```{r}

```

**Beta(20, 20):**

```{r}

```


**a. Do these priors have the same mean? Provide appropriate statistical justification in your response.**



**b. What can you see about the *strength* of the priors?**



**2. Suppose a survey yields 4 successes out of 10 responses. Find the posterior distributions with the following priors:**

**Beta(2, 2):**

```{r}

```

**Beta(20, 20):**

```{r}

```

**Comparison:**

<!-- what is similar? what is different? how did the different shapes/strengths of the priors affect the posterior? is this logical given your answer to 1b? -->

**3. The restaurant owner finds information from the previous analysis, where his belief about the proportion of students' favorite dining day being Friday was represented by a Beta(15, 10) distribution, resulted from a prior of Beta(3, 2) and survey results $y=12$ and $n=20$. The owner now wants to conduct another dining survey with the same question: Is Friday your favorite dining day?**

**a. The second survey gives a result of 8 yes out of 20 responses. Use the owner’s current beliefs and this information to update the restaurant owner’s belief about the proportion proportion, $\pi$.**

**Prior:** Beta(15, 10)

**Posterior:** <!-- insert your posterior here please -->

```{r}

```

**b. Let's look at analyzing the combined data. Start with the initial prior of Beta(3, 2) and find the posterior distribution for $y=12+8=20$ out of $n=20+20=40$ responses.**

**Prior:** Beta(3, 2)

**Posterior:** <!-- insert your posterior here please -->

```{r}

```

**c. Are the two posterior distribution the same in parts (a) and (b)? Why or why not?**



**d. Suppose the two survey results are reversed. That is, the first survey gives 8 yes and second survey gives 12 yes. Do you still observe the same posterior as in part (b)? Why or why not?**

```{r}

```

**e. Suppose the two survey results are slightly different: the first survey gives 15 yes and the second survey gives 5 yes. What is the posterior distribution in this case?**

**Prior:** Beta(3, 2)

**Posterior:** <!-- insert your posterior here please -->

```{r}

```

**4. Should we combine the two survey results together? Why or why not?** 



**5. Describe a scenario where you believe it would be inappropriate to combine the survey results.**



